### 2018-07-02 doc/plos/text/manuscript.tex
add subsection for data sources

@@

>>>>

\subsection*{Data Sources}

Data sources used in nowcasting can be broadly separated into two classes:
ground truth and surveillance. The aim at any given point in time is to predict
ground truth, given surveillance. Surveillance can be further divided into
digital surveillance (e.g. based on social media) and predictive surveillance
(e.g. based on short-term forecasts). Below are the specific data sources we
use in each category.

\subsubsection*{Ground Truth}

\begin{description}
  \item{\textbf{Population weighted percent Influenza-like Illness (wILI)}} \\
    Each week, CDC publishes wILI for the US as a whole, the 10 HHS regions,
    the 9 census divisions, and most states and territories \cite{wilisrc}. In
    any given location, wILI is the mean (weighted by population) of ILI in
    constituent locations. ILI is the percent of influenza-like illness out of
    all patient visits voluntarily reported by participating healthcare
    providers. Because reports continue to be integrated after initial
    publication, wILI is subject to retrospective revision in a process we
    refer to as ``backfill''. As a result, wILI is effectively versioned. When
    training models and making predictions, we use preliminary---not
    final---values of wILI whenever possible.
\end{description}

\subsubsection*{Digital Surveillance}

\begin{description}
  \item{\textbf{Google Flu Trends}} \\
    Google Flu Trends was a weekly prediction of wILI based on Google searches.
    The service was originally released in 2008; was updated in 2009, 2013, and
    2014 \cite{ginsberg2009, gft_main}; and was discontinued in 2015.
  \item{\textbf{Google Health Trends}} \\
    Google Health Trends is an API by Google for research purposes which makes
    available, among many other things, daily counts (on an arbitrary scale)
    for a predefined influenza topic. TODO(link)
  \item{\textbf{HealthTweets}} \\
    HealthTweets (http://healthtweets.org) makes available the daily volume of
    tweets indicative of ILI \cite{broniatowski2013national,
    dredze2014healthtweets}.
  \item{\textbf{Wikimedia Foundation}} \\
    The Wikimedia Foundation makes available the number of hits, per hour, to
    every Wikipedia article. TODO(link)
  \item{\textbf{CDC Page Hits}} \\
    CDC makes available the number of daily hits per page, per state for their
    website (https:/www.cdc.gov/).
\end{description}

\subsubsection*{Predictive Surveillance}

\begin{description}
  \item{\textbf{Epicast (EPIC)}} \\
    Epicast \cite{farrow2017human} is an influenza forecasting system based on
    collective human judgment. From these forecasts, we interpret the
    one-week-ahead value of wILI as a nowcast. TODO(link)
  \item{\textbf{Seasonal Autoregression (SAR3)}} \\
    SAR3 \cite{farrow2016modeling} provides an autoregression estimate of wILI
    on the current week. TODO(link)
  \item{\textbf{Epidemic Archetype (ARCH)}} \\
    ARCH \cite{farrow2016modeling} is an empirical model based on the Empirical
    Bayes forecasting framework \cite{brooks2015}. Like Epicast, ARCH provides
    a short-term epidemiological forecast from which we interpret the
    one-week-ahead prediction as a nowcast.
\end{description}

With the exception of Google Health Trends, these data sources are publicly
available via the Delphi Epidata API. TODO(can we share TWTR? GHT?) TODO(link)

\subsection*{Fitting}

%As others have done for flu and other infectious diseases
%\cite{generous2014global, hickmann2015forecasting, mciver2014wikipedia}, we use
%the popularity of selected articles to estimate wILI for the US as a whole.
%
%As with WIKI, we use popularity of selected pages to estimate ILI within US
%states.
%
%Inputs available at sub-weekly temporal resolution are aggregated to form
%weekly readings.

@@

\bibitem{wilisrc}
Influenza National and Regional Level Graphs and Data; 2017.
\newblock Available from:
  \url{https://gis.cdc.gov/grasp/fluview/fluportaldashboard.html}.

\bibitem{gft_main}
Google Flu Trends; 2015.
\newblock Available from: \url{https://www.google.org/flutrends/about/}.

\bibitem{dredze2014healthtweets}
Dredze M, Cheng R, Paul MJ, Broniatowski D.
\newblock HealthTweets.org: a platform for public health surveillance using
  twitter.
\newblock In: AAAI Conference on Artificial Intelligence; 2014. p. 1--2.
